Supplementary material for "Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-09-22 manuscript/manuscript.Rmd
Fixup errors

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
?library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitr")
library("kfigr")
library("knitcitations")
library("parallel")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_reliability)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1, fig.align="center")
options(mc.cores = parallel::detectCores())
```

>>>>

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitr")
library("kfigr")
library("knitcitations")
library("parallel")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_reliability)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1, fig.align="center")
options(mc.cores = parallel::detectCores())
```

### 2015-09-22 manuscript/supplement.Rmd
Fixup errors

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitr")
library("kfigr")
library("knitcitations")
library("parallel")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_reliability)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1, fig.align="center")
```

@@

@@

```{r geomorph_consistency, warning=FALSE}
res <- gpa_with_vectors(only_good_points, family, role, sha1mac, sequence)

@@

devtools::install_version("geomorph", version = "2.1.6", local=F, quick=T, dependencies=F, upgrade_dependencies=F, keep_source=T)

devtools::install("~/geomorph/", local=F, quick=T, dependencies=F, upgrade_dependencies=F, keep_source=T)

lm_result <- advanced.procD.lm(res$coords ~ family*role*sha1mac, ~family*sha1mac, iter=9)
?lm_p <- lm_result$P[2]
lm_Z <- lm_result$Z[2]
lm_F <- lm_result$F[2]
rm(family, role, repno, sha1mac)
```

![Landmarks (J1) rostral tip of premaxilla (J2) ventral tip of premaxilla (J3) rostral tip of dentary (E1) anterior margin of midline through eye (E2) posterior margin of midline through eye (O1) dorsal end of preopercle (O2) ventral elbow of preopercle (O3) anterior end of preopercle (O4) dorsal end of opercle (O5) posterior end of opercle (D1) anterior insertion of dorsal fin (D2) distal tip of the anterior dorsal fin ray (D3) distal tip of the posterior dorsal fin ray (D4) posterior insertion of dorsal fin (P1) dorsal insertion of pectoral fin (P2) distal tip of the dorsal pectoral fin ray (P3) distal tip of the ventral pectoral fin ray (P4) ventral insertion of anal fin (A1) anterior insertion of anal fin (A2) distal tip of the anterior anal fin ray (A3) distal tip of the posterior anal fin ray (A4) posterior insertion of anal fin (C1) dorsal insertion of the caudal fin (C2) distal tip of the dorsal caudal fin ray (C3) distal tip of the the ventral caudal fin ray (C4) ventral insertion of the caudal fin (C5) midpoint of the caudal margin of the caudal peduncle](landmark_figure/landmarks.pdf)

@@

>>>>

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitr")
library("kfigr")
library("knitcitations")
library("parallel")
library("fish.reliability")
options("citation_format"="pandoc", width=88)
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_reliability)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1, fig.align="center")
```

@@

## Landmarks used

The landmarks used are shown in Supplemental Figure S2. The image is redrawn from @Chakrabarty2005, which was itself redrawn from @Nelson1994.

![Landmarks (J1) rostral tip of premaxilla (J2) ventral tip of premaxilla (J3) rostral tip of dentary (E1) anterior margin of midline through eye (E2) posterior margin of midline through eye (O1) dorsal end of preopercle (O2) ventral elbow of preopercle (O3) anterior end of preopercle (O4) dorsal end of opercle (O5) posterior end of opercle (D1) anterior insertion of dorsal fin (D2) distal tip of the anterior dorsal fin ray (D3) distal tip of the posterior dorsal fin ray (D4) posterior insertion of dorsal fin (P1) dorsal insertion of pectoral fin (P2) distal tip of the dorsal pectoral fin ray (P3) distal tip of the ventral pectoral fin ray (P4) ventral insertion of anal fin (A1) anterior insertion of anal fin (A2) distal tip of the anterior anal fin ray (A3) distal tip of the posterior anal fin ray (A4) posterior insertion of anal fin (C1) dorsal insertion of the caudal fin (C2) distal tip of the dorsal caudal fin ray (C3) distal tip of the the ventral caudal fin ray (C4) ventral insertion of the caudal fin (C5) midpoint of the caudal margin of the caudal peduncle.](landmark_figure/landmarks.pdf)

@@

```{r geomorph_consistency, warning=FALSE}
only_good_points <- fish_reliability %>% filter(role != "student", !mark %in% c("A3", "A4", "D3", "D4", "O1", "O2", "O3","O4","O5", "P3", "P4"))
res <- gpa_with_vectors(only_good_points, family, role, sha1mac, sequence)

@@

lm_result <- advanced.procD.lm(res$coords ~ family*role*sha1mac, ~family*sha1mac, .parallel.cores = 24, .parallel.cluster = parallel::makeForkCluster(24))
lm_p <- lm_result$P[2]
lm_Z <- lm_result$Z[2]
lm_F <- lm_result$F[2]
rm(family, role, repno, sha1mac)
```

We also used a non-parametric MANOVA with RRPP to determine whether turkers were less consistent among individual replicates as compared to experts. The non-parametric MANOVA with RRPP failed to detect a significant difference between turker and expert shapes ($p = `r lm_p`$, $Z = `r lm_Z`$, $F=`r lm_F`$).

## R information

Information on the versions of R packages used to analyze this data.

```{r session_info}
devtools::session_info()
```

@@

## References
